Dosage forms in antibiotic PDEs

### 2017-02-21 dosage-form/dosage-form.Rmd
keeping a codes-to-keep list
fixed scan
removed drops

```{r load_library, echo=FALSE}
library(knitr)
```

```{r load_data, message=FALSE}
dat = 2011:2014 %>%
  lapply(function(y) read_tsv(sprintf('../abx_pde_%g.tsv', y)) %>%
           select(dosage_form_code=GCDF, dosage_form_desc=GCDF_DESC) %>%
           mutate(year=y)) %>%
  bind_rows()
```

Most codes have a unique descriptions. There are a few exceptions:
```{r code_desc}
filter_repeated_block = function(x) {
  if (nrow(x) == 1) {
    data_frame()
  } else {
    x
  }
}

dat %>%
  select(dosage_form_code, dosage_form_desc) %>%
  distinct %>%
  group_by(dosage_form_code) %>%
  do(filter_repeated_block(.)) %>%
  arrange(dosage_form_code, dosage_form_desc) %>%
  kable
```

I like the first of each of these sets, so that's the ones I'll keep.

```{r codes_by_year}
canonical_codes = dat %>%
  select(dosage_form_code, dosage_form_desc) %>%
  distinct %>%
  arrange(dosage_form_code, dosage_form_desc) %>%
  group_by(dosage_form_code) %>%
  do(head(., 1))

codes_by_year = dat %>%
  select(dosage_form_code, year) %>%
  group_by(year) %>%
  count(dosage_form_code) %>%
  spread(year, n) %>%
  left_join(canonical_codes, by='dosage_form_code') %>%
  arrange(desc(`2011`)) %>%
  kable
```

@@

```{r drugs_by_code, message=FALSE}
pde11 = read_tsv('../abx_pde_2011.tsv')

drugs_by_code = pde11 %>%
  select(generic_name=GNN, dosage_form_code=GCDF) %>%
  group_by(dosage_form_code) %>%
  count(generic_name) %>%
  group_by(dosage_form_code) %>%
  do(head(., 3))

codes_to_keep = c('AF', 'CA', 'CE', 'CJ', 'HH',
                  'HK', 'HM', 'HP', 'HQ', 'HS',
                  'HV', 'IF', 'IG', 'PD', 'PI',
                  'PP', 'QI', 'RG', 'RH', 'SC',
                  'SJ', 'SN', 'SO', 'ST', 'TA',
                  'TC', 'TE', 'TM', 'TS', 'UP',
                  'ZD')

>>>>

```{r load_data, message=FALSE}
dat = 2011:2014 %>%
  lapply(function(y) read_tsv(sprintf('../../data/pde_%i.tsv', y)) %>%
           select(generic_name=GNN, dosage_form_code=GCDF, dosage_form_desc=GCDF_DESC) %>%
           mutate(year=y)) %>%
  bind_rows()
```

Most codes have a unique descriptions.
```{r code_desc}
filter_repeated_block = function(x) {
  if (nrow(x) == 1) {
    data_frame()
  } else {
    x
  }
}

unique_combos = dat %>%
  select(dosage_form_code, dosage_form_desc) %>%
  distinct

unique_combos %>% kable
```

There are a few exceptions:

```{r repeated_codes}
unique_combos %>%
  group_by(dosage_form_code) %>%
  do(filter_repeated_block(.)) %>%
  arrange(dosage_form_code, dosage_form_desc) %>%
  kable
```

None of these repetitions are meaningfully different from one another, so I'll
conclude that the code uniquely identifies the dosage type.

```{r codes_by_year}
canonical_codes = unique_combos %>%
  group_by(dosage_form_code) %>%
  do(head(., 1))

dat %>%
  select(dosage_form_code, year) %>%
  group_by(year) %>%
  count(dosage_form_code) %>%
  spread(year, n) %>%
  left_join(canonical_codes, by='dosage_form_code') %>%
  arrange(desc(`2011`)) %>%
  kable
```

@@

```{r drugs_by_code, message=FALSE}

drugs_by_code = dat %>%
  filter(year == 2011) %>%
  select(generic_name, dosage_form_code) %>%
  group_by(dosage_form_code) %>%
  count(generic_name) %>%
  group_by(dosage_form_code) %>%
  do(head(., 3))

codes_to_keep = scan('oral_injected_codes.txt', what=character())
